### 2023-09-04 proofs/tex/decl-subtyping-lemmas.tex
Grammar update: Γ = set

\begin{lemma}[Decomposition of quantifier rules]
  \label{lemma:quant-rule-decomposition}
  Assuming that $[[pas]]$, $[[pbs]]$, $[[nas]]$, and $[[nas]]$ are disjoint from $[[Γ]]$,
  \begin{itemize}
    \item [$-_{R}$] $[[Γ ⊢ iN ≤ ∀pbs.iM]]$ holds if and only if $[[Γ, pbs ⊢ iN ≤ iM]]$;
    \item [$+_{R}$] $[[Γ ⊢ iP ≥ ∃nbs.iQ]]$ holds if and only if $[[Γ, nbs ⊢ iP ≥ iQ]]$;
    \item [$-_{L}$] suppose $[[iM]] \neq [[∀]]\dots$
      then $[[Γ ⊢ ∀pas.iN ≤ iM]]$ holds if and only if $[[Γ ⊢ [iPs/pas]iN ≤ iM]]$
      for some $[[Γ ⊢ iPs]]$;
    \item [$+_{L}$] suppose $[[iQ]] \neq [[∃]]\dots$
      then $[[Γ ⊢ ∃nas.iP ≥ iQ]]$ holds if and only if $[[Γ ⊢ [iNs/nas]iP ≥ iQ]]$
      for some $[[Γ ⊢ iNs]]$.
  \end{itemize}
\end{lemma}
\begin{proof}
  \hfill
  \begin{itemize}
    \item [$-_{R}$] Let us prove both directions. 
      \begin{itemize}
        \item [$\Rightarrow$] Let us assume $[[Γ ⊢ iN ≤ ∀pbs.iM]]$.
          $[[Γ ⊢ iN ≤ ∀pbs.iM]]$.
          Let us decompose $[[iM]]$ as $[[∀pbs'.iM']]$ where $[[iM']]$ does not start with $[[∀]]$, 
          and decompose $[[iN]]$ as $[[∀pas.iN']]$ where $[[iN']]$ does not start with $[[∀]]$.
          If $[[pbs]]$ is empty, then $[[Γ, pbs ⊢ iN ≤ iM]]$ holds by assumption.
          Otherwise, $[[Γ ⊢ ∀pas.iN' ≤ ∀pbs.∀pbs'.iM]]$ is inferred by
          \ruleref{\ottdruleDOneForallLabel}, and by inversion:
          $[[Γ,pbs,pbs' ⊢ [iPs/pas]iN' ≤ iM']]$ for some $[[Γ,pbs,pbs' ⊢ iPs]]$.
          Then again by \ruleref{\ottdruleDOneForallLabel} with the same $[[iPs]]$,
          $[[Γ,pbs ⊢ ∀pas.iN' ≤ ∀pbs'.iM']]$, that is $[[Γ,pbs ⊢ iN ≤ iM]]$.
        \item [$\Leftarrow$] let us assume $[[Γ, pbs ⊢ iN ≤ iM]]$, and let us decompose 
          $[[iN]]$ as $[[∀pas.iN']]$ where $[[iN']]$ does not start with $[[∀]]$, 
          and $[[iM]]$ as $[[∀pbs'.iM']]$ where $[[iM']]$ does not start with $[[∀]]$.
          if $[[pas]]$ and $[[pbs']]$ are empty then $[[Γ, pbs ⊢ iN ≤ iM]]$
          is turned into $[[Γ ⊢ iN ≤ ∀pbs.iM]]$ by \ruleref{\ottdruleDOneForallLabel}.
          Otherwise, $[[Γ, pbs ⊢ ∀pas.iN' ≤ ∀pbs'.iM']]$ is inferred by
          \ruleref{\ottdruleDOneForallLabel}, that is $[[Γ, pbs, pbs' ⊢ [iPs/pas]iN' ≤ iM']]$
          for some $[[Γ, pbs, pbs' ⊢ iPs]]$.
          Then by \ruleref{\ottdruleDOneForallLabel} again,
          $[[Γ ⊢ ∀pas.iN' ≤ ∀pbs,pbs'.iM']]$, in other words, $[[Γ ⊢ ∀pas.iN' ≤ ∀pbs.∀pbs'.iM']]$, 
          that is $[[Γ ⊢ iN ≤ ∀pbs.iM]]$.

      \end{itemize}
    \item [$-_{L}$] Suppose $[[iM]] \neq [[∀]]\dots$. Let us prove both directions.
      \begin{itemize}
        \item [$\Rightarrow$] Let us assume $[[Γ ⊢ ∀pas.iN ≤ iM]]$.
          then if $[[pas = ·]]$, $[[Γ ⊢ iN ≤ iM]]$ holds immediately.
          Otherwise, let us decompose  $iN$ as $[[∀pas'.iN']]$ where 
          $[[iN']]$ does not start with $[[∀]]$.
          Then $[[Γ ⊢ ∀pas.∀pas'.iN' ≤ iM']]$ is inferred by
          \ruleref{\ottdruleDOneForallLabel},
          and by inversion, 
          there exist $[[Γ ⊢ iPs,iPs']]$ 
          such that $[[Γ ⊢ [iPs/pas][iPs'/pas']iN' ≤ iM']]$ 
          (the decomposition of substitutions is possible since $[[{pas} ∩ {Γ} = ∅]]$).
          Then by \ruleref{\ottdruleDOneForallLabel} again,
          $[[Γ ⊢ ∀pas'.[iPs'/pas']iN' ≤ iM']]$ (notice that $[[ [iPs'/pas']iN' ]]$ cannot
          start with $[[∀]]$).
        \item [$\Leftarrow$] Let us assume 
          $[[Γ ⊢ [iPs/pas]iN ≤ iM]]$ for some $[[Γ ⊢ iPs]]$.
          let us decompose $iN$ as $[[∀pas'.iN']]$ where $[[iN']]$ does not start with $[[∀]]$.
          Then $[[Γ ⊢ [iPs/pas]∀pas'.iN' ≤ iM']]$ or, equivalently,
          $[[Γ ⊢ ∀pas'.[iPs/pas]iN' ≤ iM']]$ is inferred by \ruleref{\ottdruleDOneForallLabel}
          (notice that $[[ [iPs/pas]iN' ]]$ cannot start with $[[∀]]$).
          By inversion, there exist $[[Γ ⊢ iPs']]$ such that 
          $[[Γ ⊢ [iPs'/pas'][iPs/pas]iN' ≤ iM']]$. Since $[[pas']]$ is disjoint
          from the free variables of $[[iPs]]$ and from $[[pas]]$, the composition of 
          $[[iPs'/pas']]$ and $[[iPs/pas]]$ can be joined into a single substitution
          well-formed in $[[Γ]]$. Then by \ruleref{\ottdruleDOneForallLabel} again,
          $[[Γ ⊢ ∀pas.iN ≤ iM]]$.
      \end{itemize}
      \item [$+$] The positive cases are proved symmetrically.
  \end{itemize}
\end{proof}

@@

  By inversion  of $[[Γ1 ⊢ ∃nas.iP ≥ ∃nbs.iQ]]$, 
  we obtain $[[σ]]$ such that $[[ Γ1, nbs ⊢ σ : nas]]$
  and $[[Γ1, nbs ⊢ [σ]iP ≥ iQ]]$.
  By \cref{lemma:fv-propagation}, $[[fv([σ]iP) ⊆ fv(iQ)]]$.

  From the well-formedness statements 
  $[[Γi ⊢ ∃nas.iP]]$ and $[[Γi ⊢ ∃nbs.iQ]]$ we have:
  \begin{itemize}
    \item $[[Γ1, nas ⊢ iP]]$, which also means $[[Γ1, nbs ⊢ [σ]iP]]$
      by \cref{lemma:wf-subst};
    \item $[[Γ2, nas ⊢ iP]]$;
    \item $[[Γ1, nbs ⊢ iQ]]$; and 
    \item $[[Γ2, nbs ⊢ iQ]]$, which means $[[ fv(iQ) ⊆ {Γ2, nbs} ]]$
      by \cref{lemma:wf-soundness},
      and  combining it with $[[fv([σ]iP) ⊆ fv(iQ)]]$, 
      we have $[[fv([σ]iP) ⊆ {Γ2, nbs}]]$.
  \end{itemize}

@@

    \item $[[ Ord fv([σ]iP) ⊢ σ0 : nas]]$.
      To show that, let us consider $[[αi⁻]]$ 
      \begin{itemize}
        \item if $[[αi⁻ ∊ {nas} \ fv(iP)]]$ then
          $[[· ⊢ [σ0]αi⁻]]$, which can be weakened to 
          $[[Ord fv([σ]iP) ⊢ [σ0]αi⁻]]$;
        \item if $[[αi⁻ ∊ {nas} ∩ fv(iP)]]$, 
          we have $[[ [σ0]αi⁻ = [σ]αi⁻ ]]$, and thus, by
          specification of $[[σ]]$, $[[Γ1, pbs ⊢ [σ0]αi⁻ ]]$. 
          By \cref{corollary:wf-ctxt-strengthening}, 
          it means $[[Ord fv([σ0]αi⁻) ⊢ [σ0]αi⁻]]$,
          which we weaken (\cref{lemma:wf-weakening}) 
          to $[[Ord fv([σ]iP) ⊢ [σ0]αi⁻]]$ 
          (since $[[fv([σ0]αi⁻) ⊆ fv([σ0]iP)]]$ by \cref{lemma:subst-fv-image},
          and $[[ [σ0]iP = [σ]iP]]$, as noted above).
      \end{itemize} 
  \end{enumerate}

  By \cref{corollary:wf-ctxt-strengthening}, 
  $[[Γ1, nbs ⊢ [σ]iP]]$ implies 
  $[[ Ord fv([σ]iP) ⊢ [σ]iP ]]$, which,
  since $[[fv([σ]iP) ⊆ {Γ2, nbs}]]$,
  is weakened to $[[Γ2, nbs ⊢ [σ]iP]]$.
  and rewritten as $[[Γ2, nbs ⊢ [σ0]iP]]$.

  Notice that the premises of the induction hold:
  \begin{enumerate}
    \item $[[Γi, nbs ⊢ [σ0]iP]]$, 
    \item $[[Γi, nbs ⊢ iQ]]$, and
    \item $[[Γ1, nbs ⊢ [σ0]iP ≥ iQ ]]$, 
      notice that the tree inferring this judgement 
      is the same tree inferring $[[Γ1, nbs ⊢ [σ]iP ≥ iQ ]]$ 
      (since $[[ [σ0]iP = [σ]iP]]$), i.e., 
      it is a subtree of $[[Γ1 ⊢ ∃nas.iP ≥ ∃nbs.iQ]]$.
  \end{enumerate}
  This way, by the induction hypothesis,
  $[[Γ2, nbs ⊢ [σ0]iP ≥ iQ ]]$.
  Combining it with $[[ Γ2, nbs ⊢ σ0 : nas]]$
  by \ruleref{\ottdruleDOneExistsLabel},
  we obtain $[[Γ2 ⊢ ∃nas.iP ≥ ∃nbs.iQ]]$.

@@

\begin{lemma}[Weakening of subtyping context]
  \label{lemma:subt-weakening}
  Suppose $[[Γ1]]$ and $[[Γ2]]$ are contexts 
  and $[[ {Γ1} ⊆ {Γ2} ]]$.
  Then 
  \begin{enumerate}
    \item [$+$] $[[Γ1 ⊢ iP ≥ iQ]]$ implies $[[Γ2 ⊢ iP ≥ iQ]]$;
    \item [$-$] $[[Γ1 ⊢ iN ≤ iM]]$ implies $[[Γ2 ⊢ iN ≤ iM]]$.
  \end{enumerate}
\end{lemma}
\begin{proof}
\end{proof}

@@

  First, let us consider the 3 important cases.
  \begin{caseof}
    \item Let us consider the case when $[[iM1 = ∀pbs1.α⁻]]$. 
      Then by \cref{lemma:var-subt},
       $[[Γ ⊢ iN ≤ iM1]]$ means that $[[iN = ∀pas.α⁻]]$. 
      $[[ [σ]iM1 = [σ]iM2 ]]$ means that $[[ ∀pbs1.[σ]α⁻ = [σ]iM2 ]]$.
      Applying $[[σ]]$ to both sides of $[[Γ ⊢ iM2 ≤ iK]]$ (by \cref{lemma:subst-pres-subt}),
      we obtain $[[Γ' ⊢ [σ]iM2 ≤ [σ]iK]]$, that is $[[Γ' ⊢  ∀pbs1.[σ]α⁻ ≤ [σ]iK]]$.
      Since $[[ fv([σ]α⁻) ⊆ {Γ,α⁻} ]]$, it is disjoint from $[[pas]]$ and $[[pbs1]]$,
      This way, by \cref{corollary:red-quant-elim}, 
      $[[Γ' ⊢  ∀pbs1.[σ]α⁻ ≤ [σ]iK]]$ is equivalent to 
      $[[Γ' ⊢  [σ]α⁻ ≤ [σ]iK]]$, which is equivalent to $[[Γ' ⊢  ∀pas.[σ]α⁻ ≤ [σ]iK]]$,
      that is $[[Γ' ⊢  [σ]iN ≤ [σ]iK]]$.
    \item Let us consider the case when $[[iM2 = ∀pbs2.α⁻]]$.
      This case is symmetric to the previous one. Notice that 
      \cref{lemma:var-subt,corollary:red-quant-elim} are agnostic to the 
      side on which the the quantifiers occur, and thus, 
      the proof stays the same. 
    \item Let us decompose the types, by extracting the outer quantifiers:
      \begin{itemize}
        \item $[[iN = ∀pas.iN']]$, where $[[iN']] \neq [[∀]]\dots$,
        \item $[[iM1 = ∀pbs1.iM1']]$, where $[[iM1']] \neq [[∀]]\dots$,
        \item $[[iM2 = ∀pbs2.iM2']]$, where $[[iM2']] \neq [[∀]]\dots$,
        \item $[[iK = ∀pcs.iK']]$, where $[[iK']] \neq [[∀]]\dots$.
      \end{itemize}
      and assume that at least one of $[[pas]]$, $[[pbs1]]$, $[[pbs2]]$, and $[[pcs]]$ is not empty.
      Since $[[ [σ]iM1 = [σ]iM2 ]]$, we have $[[ ∀pbs1.[σ]iM1' = ∀pbs2.[σ]iM2' ]]$,
      and since $[[iMi']]$ are not variables 
      (which was covered by the previous cases) and do not start with $\forall$,
      $[[ [σ]iMi' ]]$ do not start with $\forall$ either,
      which means $[[pbs1]] = [[pbs2]]$ and $[[ [σ]iM1' = [σ]iM2' ]]$.
      Let us rename $[[pbs1]]$ and $[[pbs2]]$ to $[[pbs]]$.
      Then $[[iM1 = ∀pbs.iM1']]$ and $[[iM2 = ∀pbs.iM2']]$.

>>>>

\begin{lemma}[Decomposition of quantifier rules]
  \label{lemma:quant-rule-decomposition}
  Assuming that $[[pas]]$, $[[pbs]]$, $[[nas]]$, and $[[nas]]$ are disjoint from $[[Γ]]$,
  \begin{itemize}
    \item [$-_{R}$] $[[Γ ⊢ iN ≤ ∀pbs.iM]]$ holds if and only if $[[Γ, pbs ⊢ iN ≤ iM]]$;
    \item [$+_{R}$] $[[Γ ⊢ iP ≥ ∃nbs.iQ]]$ holds if and only if $[[Γ, nbs ⊢ iP ≥ iQ]]$;
    \item [$-_{L}$] suppose $[[iM]] \neq [[∀]]\dots$
      then $[[Γ ⊢ ∀pas.iN ≤ iM]]$ holds if and only if $[[Γ ⊢ [iPs/pas]iN ≤ iM]]$
      for some $[[Γ ⊢ iPs]]$;
    \item [$+_{L}$] suppose $[[iQ]] \neq [[∃]]\dots$
      then $[[Γ ⊢ ∃nas.iP ≥ iQ]]$ holds if and only if $[[Γ ⊢ [iNs/nas]iP ≥ iQ]]$
      for some $[[Γ ⊢ iNs]]$.
  \end{itemize}
\end{lemma}
\begin{proof}
  \hfill
  \begin{itemize}
    \item [$-_{R}$] Let us prove both directions. 
      \begin{itemize}
        \item [$\Rightarrow$] Let us assume $[[Γ ⊢ iN ≤ ∀pbs.iM]]$.
          $[[Γ ⊢ iN ≤ ∀pbs.iM]]$.
          Let us decompose $[[iM]]$ as $[[∀pbs'.iM']]$ where $[[iM']]$ does not start with $[[∀]]$, 
          and decompose $[[iN]]$ as $[[∀pas.iN']]$ where $[[iN']]$ does not start with $[[∀]]$.
          If $[[pbs]]$ is empty, then $[[Γ, pbs ⊢ iN ≤ iM]]$ holds by assumption.
          Otherwise, $[[Γ ⊢ ∀pas.iN' ≤ ∀pbs.∀pbs'.iM]]$ is inferred by
          \ruleref{\ottdruleDOneForallLabel}, and by inversion:
          $[[Γ, {pbs}, {pbs'} ⊢ [iPs/pas]iN' ≤ iM']]$ for some $[[Γ, {pbs}, {pbs'} ⊢ iPs]]$.
          Then again by \ruleref{\ottdruleDOneForallLabel} with the same $[[iPs]]$,
          $[[Γ,pbs ⊢ ∀pas.iN' ≤ ∀pbs'.iM']]$, that is $[[Γ,pbs ⊢ iN ≤ iM]]$.
        \item [$\Leftarrow$] let us assume $[[Γ, pbs ⊢ iN ≤ iM]]$, and let us decompose 
          $[[iN]]$ as $[[∀pas.iN']]$ where $[[iN']]$ does not start with $[[∀]]$, 
          and $[[iM]]$ as $[[∀pbs'.iM']]$ where $[[iM']]$ does not start with $[[∀]]$.
          if $[[pas]]$ and $[[pbs']]$ are empty then $[[Γ, pbs ⊢ iN ≤ iM]]$
          is turned into $[[Γ ⊢ iN ≤ ∀pbs.iM]]$ by \ruleref{\ottdruleDOneForallLabel}.
          Otherwise, $[[Γ, pbs ⊢ ∀pas.iN' ≤ ∀pbs'.iM']]$ is inferred by
          \ruleref{\ottdruleDOneForallLabel}, that is $[[Γ, {pbs}, {pbs'} ⊢ [iPs/pas]iN' ≤ iM']]$
          for some $[[Γ, {pbs}, {pbs'} ⊢ iPs]]$.
          Then by \ruleref{\ottdruleDOneForallLabel} again,
          $[[Γ ⊢ ∀pas.iN' ≤ ∀pbs,pbs'.iM']]$, in other words, $[[Γ ⊢ ∀pas.iN' ≤ ∀pbs.∀pbs'.iM']]$, 
          that is $[[Γ ⊢ iN ≤ ∀pbs.iM]]$.

      \end{itemize}
    \item [$-_{L}$] Suppose $[[iM]] \neq [[∀]]\dots$. Let us prove both directions.
      \begin{itemize}
        \item [$\Rightarrow$] Let us assume $[[Γ ⊢ ∀pas.iN ≤ iM]]$.
          then if $[[pas = ·]]$, $[[Γ ⊢ iN ≤ iM]]$ holds immediately.
          Otherwise, let us decompose  $iN$ as $[[∀pas'.iN']]$ where 
          $[[iN']]$ does not start with $[[∀]]$.
          Then $[[Γ ⊢ ∀pas.∀pas'.iN' ≤ iM']]$ is inferred by
          \ruleref{\ottdruleDOneForallLabel},
          and by inversion, 
          there exist $[[Γ ⊢ iPs,iPs']]$ 
          such that $[[Γ ⊢ [iPs/pas][iPs'/pas']iN' ≤ iM']]$ 
          (the decomposition of substitutions is possible since $[[{pas} ∩ Γ = ∅]]$).
          Then by \ruleref{\ottdruleDOneForallLabel} again,
          $[[Γ ⊢ ∀pas'.[iPs'/pas']iN' ≤ iM']]$ (notice that $[[ [iPs'/pas']iN' ]]$ cannot
          start with $[[∀]]$).
        \item [$\Leftarrow$] Let us assume 
          $[[Γ ⊢ [iPs/pas]iN ≤ iM]]$ for some $[[Γ ⊢ iPs]]$.
          let us decompose $iN$ as $[[∀pas'.iN']]$ where $[[iN']]$ does not start with $[[∀]]$.
          Then $[[Γ ⊢ [iPs/pas]∀pas'.iN' ≤ iM']]$ or, equivalently,
          $[[Γ ⊢ ∀pas'.[iPs/pas]iN' ≤ iM']]$ is inferred by \ruleref{\ottdruleDOneForallLabel}
          (notice that $[[ [iPs/pas]iN' ]]$ cannot start with $[[∀]]$).
          By inversion, there exist $[[Γ ⊢ iPs']]$ such that 
          $[[Γ ⊢ [iPs'/pas'][iPs/pas]iN' ≤ iM']]$. Since $[[pas']]$ is disjoint
          from the free variables of $[[iPs]]$ and from $[[pas]]$, the composition of 
          $[[iPs'/pas']]$ and $[[iPs/pas]]$ can be joined into a single substitution
          well-formed in $[[Γ]]$. Then by \ruleref{\ottdruleDOneForallLabel} again,
          $[[Γ ⊢ ∀pas.iN ≤ iM]]$.
      \end{itemize}
      \item [$+$] The positive cases are proved symmetrically.
  \end{itemize}
\end{proof}

@@

  By inversion  of $[[Γ1 ⊢ ∃nas.iP ≥ ∃nbs.iQ]]$, 
  we obtain $[[σ]]$ such that $[[ Γ1, nbs ⊢ σ :{nas}]]$
  and $[[Γ1, nbs ⊢ [σ]iP ≥ iQ]]$.
  By \cref{lemma:fv-propagation}, $[[fv([σ]iP) ⊆ fv(iQ)]]$.

  From the well-formedness statements 
  $[[Γi ⊢ ∃nas.iP]]$ and $[[Γi ⊢ ∃nbs.iQ]]$ we have:
  \begin{itemize}
    \item $[[Γ1, nas ⊢ iP]]$, which also means $[[Γ1, nbs ⊢ [σ]iP]]$
      by \cref{lemma:wf-subst};
    \item $[[Γ2, nas ⊢ iP]]$;
    \item $[[Γ1, nbs ⊢ iQ]]$; and 
    \item $[[Γ2, nbs ⊢ iQ]]$, which means $[[ fv(iQ) ⊆ Γ2, nbs ]]$
      by \cref{lemma:wf-soundness},
      and  combining it with $[[fv([σ]iP) ⊆ fv(iQ)]]$, 
      we have $[[fv([σ]iP) ⊆ Γ2, nbs]]$.
  \end{itemize}

@@

    \item $[[  fv([σ]iP) ⊢ σ0 :{nas}]]$.
      To show that, let us consider $[[αi⁻]]$ 
      \begin{itemize}
        \item if $[[αi⁻ ∊ {nas} \ fv(iP)]]$ then
          $[[· ⊢ [σ0]αi⁻]]$, which can be weakened to 
          $[[ fv([σ]iP) ⊢ [σ0]αi⁻]]$;
        \item if $[[αi⁻ ∊ {nas} ∩ fv(iP)]]$, 
          we have $[[ [σ0]αi⁻ = [σ]αi⁻ ]]$, and thus, by
          specification of $[[σ]]$, $[[Γ1, pbs ⊢ [σ0]αi⁻ ]]$. 
          By \cref{corollary:wf-ctxt-strengthening}, 
          it means $[[ fv([σ0]αi⁻) ⊢ [σ0]αi⁻]]$,
          which we weaken (\cref{lemma:wf-weakening}) 
          to $[[ fv([σ]iP) ⊢ [σ0]αi⁻]]$ 
          (since $[[fv([σ0]αi⁻) ⊆ fv([σ0]iP)]]$ by \cref{lemma:subst-fv-image},
          and $[[ [σ0]iP = [σ]iP]]$, as noted above).
      \end{itemize} 
  \end{enumerate}

  By \cref{corollary:wf-ctxt-strengthening}, 
  $[[Γ1, nbs ⊢ [σ]iP]]$ implies 
  $[[  fv([σ]iP) ⊢ [σ]iP ]]$, which,
  since $[[fv([σ]iP) ⊆ Γ2, nbs]]$,
  is weakened to $[[Γ2, nbs ⊢ [σ]iP]]$.
  and rewritten as $[[Γ2, nbs ⊢ [σ0]iP]]$.

  Notice that the premises of the induction hold:
  \begin{enumerate}
    \item $[[Γi, nbs ⊢ [σ0]iP]]$, 
    \item $[[Γi, nbs ⊢ iQ]]$, and
    \item $[[Γ1, nbs ⊢ [σ0]iP ≥ iQ ]]$, 
      notice that the tree inferring this judgement 
      is the same tree inferring $[[Γ1, nbs ⊢ [σ]iP ≥ iQ ]]$ 
      (since $[[ [σ0]iP = [σ]iP]]$), i.e., 
      it is a subtree of $[[Γ1 ⊢ ∃nas.iP ≥ ∃nbs.iQ]]$.
  \end{enumerate}
  This way, by the induction hypothesis,
  $[[Γ2, nbs ⊢ [σ0]iP ≥ iQ ]]$.
  Combining it with $[[ Γ2, nbs ⊢ σ0 :{nas}]]$
  by \ruleref{\ottdruleDOneExistsLabel},
  we obtain $[[Γ2 ⊢ ∃nas.iP ≥ ∃nbs.iQ]]$.

@@

\begin{lemma}[Weakening of subtyping context]
  \label{lemma:subt-weakening}
  Suppose $[[Γ1]]$ and $[[Γ2]]$ are contexts 
  and $[[ Γ1 ⊆ Γ2 ]]$.
  Then 
  \begin{enumerate}
    \item [$+$] $[[Γ1 ⊢ iP ≥ iQ]]$ implies $[[Γ2 ⊢ iP ≥ iQ]]$;
    \item [$-$] $[[Γ1 ⊢ iN ≤ iM]]$ implies $[[Γ2 ⊢ iN ≤ iM]]$.
  \end{enumerate}
\end{lemma}
\begin{proof}
\end{proof}

@@

  First, let us consider the 3 important cases.
  \begin{caseof}
    \item Let us consider the case when $[[iM1 = ∀pbs1.α⁻]]$. 
      Then by \cref{lemma:var-subt},
       $[[Γ ⊢ iN ≤ iM1]]$ means that $[[iN = ∀pas.α⁻]]$. 
      $[[ [σ]iM1 = [σ]iM2 ]]$ means that $[[ ∀pbs1.[σ]α⁻ = [σ]iM2 ]]$.
      Applying $[[σ]]$ to both sides of $[[Γ ⊢ iM2 ≤ iK]]$ (by \cref{lemma:subst-pres-subt}),
      we obtain $[[Γ' ⊢ [σ]iM2 ≤ [σ]iK]]$, that is $[[Γ' ⊢  ∀pbs1.[σ]α⁻ ≤ [σ]iK]]$.
      Since $[[ fv([σ]α⁻) ⊆ Γ,α⁻ ]]$, it is disjoint from $[[pas]]$ and $[[pbs1]]$,
      This way, by \cref{corollary:red-quant-elim}, 
      $[[Γ' ⊢  ∀pbs1.[σ]α⁻ ≤ [σ]iK]]$ is equivalent to 
      $[[Γ' ⊢  [σ]α⁻ ≤ [σ]iK]]$, which is equivalent to $[[Γ' ⊢  ∀pas.[σ]α⁻ ≤ [σ]iK]]$,
      that is $[[Γ' ⊢  [σ]iN ≤ [σ]iK]]$.
    \item Let us consider the case when $[[iM2 = ∀pbs2.α⁻]]$.
      This case is symmetric to the previous one. Notice that 
      \cref{lemma:var-subt,corollary:red-quant-elim} are agnostic to the 
      side on which the the quantifiers occur, and thus, 
      the proof stays the same. 
    \item Let us decompose the types, by extracting the outer quantifiers:
      \begin{itemize}
        \item $[[iN = ∀pas.iN']]$, where $[[iN']] \neq [[∀]]\dots$,
        \item $[[iM1 = ∀pbs1.iM1']]$, where $[[iM1']] \neq [[∀]]\dots$,
        \item $[[iM2 = ∀pbs2.iM2']]$, where $[[iM2']] \neq [[∀]]\dots$,
        \item $[[iK = ∀pcs.iK']]$, where $[[iK']] \neq [[∀]]\dots$.
      \end{itemize}
      and assume that at least one of $[[pas]]$, $[[pbs1]]$, $[[pbs2]]$, and $[[pcs]]$ is not empty.
      Since $[[ [σ]iM1 = [σ]iM2 ]]$, we have $[[ ∀pbs1.[σ]iM1' = ∀pbs2.[σ]iM2' ]]$,
      and since $[[iMi']]$ are not variables 
      (which was covered by the previous cases) and do not start with $\forall$,
      $[[ [σ]iMi' ]]$ do not start with $\forall$ either,
      which means $[[pbs1]] = [[pbs2]]$ and $[[ [σ]iM1' = [σ]iM2' ]]$.
      Let us rename $[[pbs1]]$ and $[[pbs2]]$ to $[[pbs]]$.
      Then $[[iM1 = ∀pbs.iM1']]$ and $[[iM2 = ∀pbs.iM2']]$.
